\noindent Buyer power is a central issue in agricultural-product procurement markets \citep{rogers_rich_1994assessing, barrett2022agri}, reflecting the relative immobility of farm products that can make them effectively ``captive'' to a small number of buyers operating in the area \citep{merel2017buyer}. In addition, farmers in developing countries often face pressure to sell quickly at harvest because of liquidity constraints or lack of access to storage \citep{bergquist_dinerstein_2020, Kopp-Mishra, nindi2024incentive, itin2024effect}.  While impacts of spatial immobility of agricultural products on competition have been studied extensively \citep{jung2022structural, BARTKUS2022, chatterjee2023market,graubner2023more}, the impact of changes in temporal mobility of storable products on competitive outcomes is largely unexplored.

Although the literature has long recognized the importance of buyer power in agricultural-product procurement markets, it has almost invariably been treated as a static phenomenon, a durable feature of market structure shaped by market concentration, spatial dispersion of buyers, sunk costs and other barriers to entry into the packing, processing, or export sectors, and strategic behavior among buyers \citep{sexton2013market}.
This static view of buyer power is descriptive of certain agricultural industries where procurement markets are characterized by the presence of a few processing firms with large capital investments and high sunk costs, and substantial barriers to entry.\footnote{The beef processing sector in the United States represents a classic example wherein the four-firm concentration ratio has been near 85\% for several decades \citep{Moschini-Smith}.}

It is not, however, descriptive of many procurement markets in developing-country settings involving resource-constrained farmers who lack means to transport their production to expand selling options, traders who are highly mobile and make strategic procurement decisions, and weak legal institutions that make it difficult to detect and prevent collusion or enforce competition laws, if such laws exist at all \citep{sexton2018increasing}. In these settings, smallholders without access to storage are forced to sell in local markets at harvest despite potentially facing significant buyer market power.

However, buyer power in these settings may be fluid within the marketing season as traders enter and exit local markets, collusive agreements form and dissolve, and demand and supply conditions change \citep{kopp2021farmers}.\footnote{The stability of collusive arrangements among buyers, in particular, may be strongly influenced by changes in market conditions. Positive demand shocks, for example, magnify the incentive to cheat on a collusive agreement \citep{Rotemberg_1986, richards2001price, sudhir2005time}.}
Field evidence from diverse contexts confirms this temporal fluidity in competitive conditions, including procurement markets for fresh apples in China in this dissertation, tobacco in China \citep{rubens2023market}, coffee in Uganda \citep{fafchamps2005selling}, and maize across Eastern and Southern Africa \citep{sitko2014exploitative, burke2019sell}.

My dissertation adds an additional motivating factor into the economics of commodity storage. Standard frameworks treat storage as intertemporal arbitrage driven by predictable demand or supply shifts across a marketing season, while holding competitive conditions constant \citep{helmberger1977welfare, wright1982econ, wright1984welfare, deaton1992behaviour}. Several studies provide empirical evidence that storage can raise smallholder expected incomes by enabling sales in non-harvest months when prices tend to be higher \citep{aggarwal2018grain, priya2020post, ruhinduka2020smallholder}. Yet these works largely treat post-harvest price variation as exogenous or as driven by supply or demand shifts, failing to consider that the gains may in part reflect improved market competition.


On the other hand, the motivation for engaging in commodity storage has been extensively explored in the agricultural and development economics literature, with price arbitrage identified as the primary driving factor \citep{helmberger1977welfare, wright1984welfare, deaton1992behaviour, miranda1996, wright1982econ, minten2014new, nindi2024incentive}. In the context of agricultural commodities, farmers often store crops after harvest, anticipating a possible increase in price that offsets their carrying charges. Most studies have found positive welfare impacts of storage adoption. For example, \cite{ruhinduka2020smallholder} investigate storage and processing decisions, which can increase income by more than 50\%, but also bring risk and time delays. \cite{aggarwal2018grain} conducted an experimental study showing that storage interventions significantly motivate farmers to store and sell their produce at later stages and higher prices. Similarly, \cite{priya2020post} examined the decision of smallholder farmers to adopt storage as a strategic tool to increase their agricultural income by leveraging price rises during non-harvest months.

Beyond explicit price uncertainty, storage decisions are also shaped by financial considerations. For instance, \cite{janzen2024commodity} show that the opportunity cost of capital is an important determinant of inventory holdings among Illinois grain farms, with some farms behaving in line with profit-maximizing theory while others hold infra-marginal inventories for non-market reasons. However, in reality, predicting storage returns proves challenging for farmers, and the volatility in farm-gate prices can discourage them from storing crops for future sales, even when they have access to credit \citep{cardell2023price}. In addition, limited access to those quality-preserving technologies further narrows farmers' marketing window, and the fixed cost of initial storage construction often makes storage adoption prohibitive for smallholder farmers, particularly in cash crops \citep{aggarwal2018grain}. Although some developing countries provide partial subsidies, uptake remains limited due to high uncertainty and capital constraints.

Traditional explanations for agricultural storage emphasize \textit{technological} features, such as cross-year production smoothing and self-consumption needs of staple crops. For instance, \cite{saha1994household} present a household model that integrates staple-crop consumption, storage, savings, and labor decisions. Likewise, \cite{park2006risk} develops a dynamic model showing that grain's consumption role makes it attractive for precautionary storage. In this strand of the literature, storage primarily serves food security and consumption smoothing, and is therefore concentrated in staple crops.




\noindent A large and growing literature documents oligopsony power in agricultural value chains in emerging economies, typically emphasizing spatial variation in market structure and buyer concentration \citep{bergquist_dinerstein_2020, kopp2021farmers,macchiavello2021competition, rubens2023market}. The field evidence reported in these studies revels patterns of buyer entry and exit into and from local markets, shifts in buyers' procurement strategies, and episodes of buyer collusive behavior, all suggestive of time-varying buyer power within a marketing season.

Trader mobility generates temporal variation in local competitive conditions. Intermediaries often operate across multiple villages and adjust travel patterns in response to expected prices, harvest timing, and rivals' behavior. \citet{bergquist_dinerstein_2020} show that Kenyan grain traders face substantial fixed costs so only a subset of potential traders is active in a given market at a given time. As itinerant buyers enter or withdraw from local markets and working-capital constraints bind differentially, a village can move from weak competition early in the harvest period to more intensive competition later, or vice versa, over the course of a single marketing season.

Farmers' marketing decisions over time can themselves reconfigure the level of buyer competition they face. At harvest, perishable crops are typically sold at or near the farmgate, where a small number of local traders may exercise considerable buyer power \citep{Barrett_WD_1997, Kopp-Mishra}. If product is moved into central storage facilities, the location of sale is reconfigured, shifting from the field to village markets or commercial facilities. These central locations can then function much like wholesale terminal markets, attracting more buyers in total and a greater diversity of buyers and, hence, greater competition than occurs at farmgates at harvest time.

This dissertation documents these points for Fuji apple procurement in central China. Procurement at harvest is dominated by small local field buyers, who may coordinate procurement territories in a collusive manner. For apples that enter centralized cold-storage facilities, the buyer mix shifts toward non-local traders and procurement agents for large retailers and processors.\footnote{Cold storage extends farmers' marketing horizon from roughly one month at harvest time to six months under conventional facilities and close to a full year under controlled-atmosphere technology. Farmers who can store thus convert a one-shot post-harvest selling opportunity into a sequence of selling opportunities in potentially different competitive environments.} These buyers often operate with procurement quotas that limit their ability to restrict purchases in order to reduce prices.

Stochastic weather shocks also can impact competition dynamics by periodically disrupting transport conditions and, in turn, the set of buyers able to reach local markets. Prior work shows that weather disturbances shape traders' expectations about supply \citep{letta2022weather} and directly affect transportation costs \citep{mitchell2025effects}, yet their implications for local market structure are less often emphasized. In hilly or infrastructure-poor regions, heavy rains render feeder roads intermittently impassable, sharply increasing access costs and restricting procurement to buyers already located within the village \citep{dappe2024shrinking}. Evidence from low- and middle-income countries indicates that such episodic declines in road passability are common and significantly limit market access for outside traders \citep{greenham2023transport}. These barriers temporarily raise local buyer concentration and strengthen buyer power. As weather conditions normalize and roads reopen, outside traders can re-enter producing areas, competition intensifies, and buyer power recedes.



Although literature in industrial organization and operations management has delved into the interplay between storage inventory and market competition, the emphasis has largely centered on the perspective of those involved in storage as sellers \citep{leng2005game}, leaving the role of input buyers and their oligopsony power relatively unexplored. For example, \cite{li1992role} demonstrates that storage adoption could promote seller's delivery-time competition and hence increase consumers' welfare; \cite{rotemberg1989cyclical} present a model in which a duopoly uses storage to deter deviations from an implicitly collusive agreement; \cite{anand2008strategic} capture the existence of strategic inventory where buyers employ inventories to prompt sellers to reduce future prices, influencing vertical competition in a dynamic monopoly-to-monopsony model; Building upon this framework, \cite{hu2021strategic} and \cite{cai2021supply} extend the analysis by incorporating various forms of horizontal competition among sellers. While most of these works developed dynamic storage-related models to either capture inventory deterioration or allow demand variability, none has introduced the possibility of time-varying market structure change, especially on the side of buyers. 


My work aims to address these gaps. In essence, this work contributes at the intersection of industrial organization and agricultural development economics \citep{bellemare2022agricultural}, offering an innovative approach to assist small and low-income suppliers in developing nations to make more effective post-harvest decisions under oligopsony power.
